---
title: "Strategic Customer Targeting for Heart Health Supplement Market"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rio)
library(tidyverse)
library(atus)
library(plotly)
library(lubridate)
library(dygraphs)
library(stringr)
library(shiny)
library(ggiraph)
data <- import('heart_2020_cleaned.csv')
```

## Row {data-width="350"}

### Top 5 Age Categories by Total People {data-width="300"}

```{r}
df <- data.frame(AgeCategory = c("18-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74", "75-79", "80 or older"),
                 TotalPeople = c(21064, 16955, 18753, 20550, 21006, 21791, 25382, 29757, 33686, 34151, 31065, 21482, 24153))

# Order the data by TotalPeople in descending order and take the top 5
df_top5 <- df %>% 
  arrange(desc(TotalPeople)) %>% 
  head(5)
abcdoremi <- df_top5%>%
  arrange(order(AgeCategory))

abcdoremi$color <- c("grey", "#95BDFF", "grey", "#95BDFF", "#95BDFF")

p <- ggplot(abcdoremi, aes(x = AgeCategory, y = TotalPeople, fill = color)) +
  geom_bar(stat = "identity") + 
  labs(x = "Age Category", y = "Total People") +
  scale_fill_manual(values = c("#95BDFF", 'grey')) +
  theme_classic() +
  guides(fill = FALSE) 

ggplotly(p)
```

### Percentage of Heart Disease by Age Category {data-width="500"}

```{r}
p1 <- data.frame(
  AgeCategory = c("18-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74", "75-79", "80 or older"),
  total = c(21064, 16955, 18753, 20550, 21006, 21791, 25382, 29757, 33686, 34151, 31065, 21482, 24153),
  count = c(130, 133, 226, 296, 486, 744, 1383, 2202, 3327, 4101, 4847, 4049, 5449),
  percentage = c(0.6171667, 0.7844294, 1.2051405, 1.4403893, 2.3136247, 3.4142536, 5.4487432, 7.3999395, 9.8765066, 12.0084331, 15.6027684, 18.8483381, 22.5603445)
)


p10 <- ggplot(p1, aes(x = AgeCategory, y = percentage)) +
  geom_line(group = 1, color = "steelblue") +
  geom_point(color = "steelblue") +
  scale_color_continuous() + 
  labs(x = "Age Category", y = "Percentage") +
  theme_classic() 

ggplotly(p10)

```

## Row {data-width="350"}

### Percentage of People with Heart Disease by Sleep Category {data-width="300"}

```{r}

data <- data %>%
  mutate(SleepCategory = ifelse(SleepTime > 7, "Less than 7 hours", "More than 7 hours")) 

data_percent <- data %>%
  group_by(SleepCategory, HeartDisease) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

sleep1 <- data_percent%>%
  filter(HeartDisease == "Yes")

p2 <- ggplot(sleep1, aes(x=SleepCategory, y= percentage, fill=SleepCategory)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values = c("Less than 7 hours" = "#FFF89A", "More than 7 hours" = "grey")) +
  ylab("Percentage") +
  xlab("Sleep Category") +
  theme_classic() + theme(legend.position = "none")

ggplotly(p2)
```

### Percentage of People with Heart Disease by Smoking Status {data-width="300"}

```{r}
data$Smoking <- ifelse(data$Smoking == "No", "No Smoking", "Smoking")

# Calculate the percentages
data_percentages <- data %>%
  group_by(Smoking, HeartDisease) %>%
  summarise(n = n()) %>%
  mutate(percentage = n / sum(n) * 100) 

# Now, let's filter out only the rows where HeartDisease is 'Yes' or equivalent value
data_percentages <- data_percentages %>%
  filter(HeartDisease == 'Yes') # Replace 'Yes' with the correct value indicating presence of heart disease in your dataset

# Plot the graph
p3 <- ggplot(data_percentages, aes(x = Smoking, y = percentage, fill = Smoking)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values = c("No Smoking" = "grey", "Smoking" = "pink")) +
  labs(x = "Smoking", y = "Percentage")+
   theme_classic() + theme(legend.position = "none")

ggplotly(p3)
```

### Distribution of BMI Category among Individuals with Heart Disease {data-width="450"}

```{r}
data1 <- data %>%
  mutate(BMICategory = case_when(
    BMI < 18.5 ~ "Underweight",
    BMI >= 18.5 & BMI < 25 ~ "Healthy weight",
    BMI >= 25 & BMI < 30 ~ "Overweight",
    BMI >= 30 ~ "Obese"
  ))

# Calculate total count for each BMI category
total_counts <- data1 %>%
  group_by(BMICategory) %>%
  summarise(total = n(), .groups = 'drop')

# Calculate count of people with heart disease for each BMI category
heart_disease_counts <- data1 %>%
  filter(HeartDisease == "Yes") %>%
  group_by(BMICategory) %>%
  summarise(count = n(), .groups = 'drop')

# Join the two data frames together
bmi <- inner_join(heart_disease_counts, total_counts, by = "BMICategory")

# Calculate the percentage
bmi123 <- bmi %>%
  mutate(percentage = (count / total) * 100)
# Create new variable for highlighting
bmi123 <- bmi123 %>%
  mutate(Highlight = ifelse(percentage %in% tail(sort(percentage), 2), "High", "Not high"))

# Reorder factors
bmi123$BMICategory <- forcats::fct_reorder(bmi123$BMICategory, bmi123$percentage)

p4 <- ggplot(bmi123, aes(x=BMICategory, y=percentage, fill=Highlight)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values=c("High"="#BE9FE1", "Not high"="grey")) +
  theme_classic() +
  theme(legend.position="none") + 
  labs(x="BMI Category", y="Percentage")

ggplotly(p4)
```

## Row {data-width="450"}

### Potential Heart Disease Risk Groups: A Comparative Analysis of Prevalence {data-width="450"}

```{r}
# Filter the data to only those who do not have heart disease
no_heart_disease <- data1 %>% filter(HeartDisease == "No")

# Calculate the percentages
smokers_no_hd <- no_heart_disease %>% filter(Smoking == "Smoking") %>% nrow() 
overweight_no_hd <- no_heart_disease %>% filter(BMICategory %in% c("Overweight", "Obese")) %>% nrow() 

age_no_hd <- no_heart_disease %>% filter(AgeCategory %in% c("60-64", "65-69", "70-74", "75-79", "80 or older")) %>% nrow() 


sleep_no_hd <- no_heart_disease %>% filter(SleepCategory == "Less than 7 hours") %>% nrow() 


# Combine into a data frame
results <- data.frame(
  Category = c("Smokers", "Overweight/Obese", "Sleep <=7 hours", "Age 60 and older"),
  Total_People = c(smokers_no_hd, overweight_no_hd, sleep_no_hd, age_no_hd)
)
final <- results %>%
  filter(Category != 'Age 60 and older')

p5 <- ggplot(final, aes(x = Total_People , y = reorder(Category, Total_People), fill = c('#BADFDB'))) +
  geom_bar(stat = "identity") +
  xlab("Total People") +
  ylab("Risk Factors") +
  scale_fill_identity() +
  theme_classic() + theme(legend.position = "none")

ggplotly(p5)
```

### Venn Diagram Risk Factors {data-width="350"}

```{r}
library(gplots)

# Define the sets
smokers_noHD <- which(data$Smoking == "Smoking" & data$HeartDisease == "No")
lowSleep_noHD <- which(data$SleepTime < 7 & data$HeartDisease == "No")
highBMI_noHD <- which(data$BMI > 25 & data$HeartDisease == "No")

# Create a list of these sets
sets <- list("Smokers" = smokers_noHD, "Sleep <= 7 hours" = lowSleep_noHD, "Overweight/Obese" = highBMI_noHD)

# Create the Venn diagram
venn(sets)

```
